Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-02 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:
Correlative SICM and fluorescence microscopy opens up the opportunity to receive information, 
which are hidden and impossible to obtain by using one of this microscopy techniques alone. 
This is especially helpful for applications, where the reaction is not limited to \emph{one 
dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
be interesting to investigate, sowohl %german
the cell membrane with a technique, which is able to do so -- AFM \cite{}, EM \cite{}, SICM 
\cite{Hansma1989} --, als auch %german
to follow the nanoparticle into the cell or to investigate simultaneously how the cytoskeleton 
react on the addition (?) of the nanoparticle by using fluorescence microscopy methods.

% Den Teil brauchen wir ja vielleicht nicht. 
AFM, a method belonging to the scanning probe microscopy techniques, was successfully
combined to fluorescence microscopy techniques e.g. to investigate the topography of a 
cell or a part of a cell with the cytoskeleton \cite{Laishram2009,Liu2020}. But a big problem 
with this method is, that it is not the most favorable for investigating living cells in their
physiological surrounding. Certain destructive effects on the cell were found by using this 
technique \cite{}. A better fitting method for investigating living cells would be scanning 
ion conductance microscopy (SICM) \cite{Hansma1989}.

@@

Another very delicate sample, because of their three-dimensional, upright (?) structure are cilia.
Here SICM was used for investigating the topography of the cilia and the fluorescence was used to
distinguish between surface and sub-surface cilia, which could not be detected with SICM 
\cite{Zhou2018}.

@@

The SICM-nanopipette could be also used for investigating membrane rafts (Quelle) by coordinated 
manipulation of focal adhesions. The pipette was functionalized with fibronectin, gangliosides
were fluorescently labeled, the pipette deformed the focal adhesion side and the behavior of the 
fluorescently labeled gangliosides were detected. This was seen as a hint, how membrane rafts 
reacted \cite{Fuentes2012}.

@@

Beside these more or less \emph{direct} combinations and correlations, which are displaying images 
obtained by SICM and fluorescence microscopy of the same cell/same region, also \emph{indirect} 
correlations exist. They are showing images under comparable conditions and extent the 
investigation to aspects, which could not be obtained by using one technique alone. Such 
\emph{indirect} correlations were used for investigating the uptake of nanotubes \cite{Lee2013}, 
nanoparticles \cite{Gesper2017} or for investigating healthy and failing myocytes \cite{Lyon2009}. 
Nichtsdestotrotz (german)
is it important to mention, that they could just giving hints of correlations, it 
is not directly comparable with investigations of both in the same cell.

>>>>

\section{Correlating SICM and Fluorescence Microscopy}
\label{sec:correlating-sicm-and-fm}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../manuscript"
%%% End:
Correlative SICM and fluorescence microscopy opens up the opportunity to receive information, 
which are hidden and impossible to obtain by using one of this microscopy techniques alone. 
This is especially helpful for applications, where the reaction is not limited to \emph{one 
dimension}, for example when investigating the uptake of nanoparticles into cells. There it would 
be interesting to investigate both the cell membrane with a technique, which is able to do so -- 
AFM \cite{Binnig1986}, EM \cite{}, SICM \cite{Hansma1989} -- and the uptake of nanoparticles into 
cells or how the cytoskeleton react on the addition of the nanoparticle by using fluorescence 
microscopy methods.

% Den Teil brauchen wir ja vielleicht nicht. 
AFM, a method belonging to the scanning probe microscopy techniques, was successfully
combined to fluorescence microscopy techniques e.g. to investigate the topography of a 
cell or a part of a cell with the cytoskeleton \cite{Laishram2009,Liu2020}. But a big problem 
with this method is, that it is not the most favorable for investigating living cells in their
physiological surrounding. Certain destructive effects on the cell were found by using this 
technique \cite{You2000,Rheinlaender2011}. A better fitting method for investigating living cells 
would be scanning ion conductance microscopy (SICM) \cite{Hansma1989}.

@@

Another very delicate sample, because of their three-dimensional, upright structure are cilia.
Here SICM was used for investigating the topography of the cilia and the fluorescence was used to
distinguish between surface and sub-surface cilia, which could not be detected with SICM 
\cite{Zhou2018}.

@@

The SICM-nanopipette could be also used for investigating membrane rafts 
\cite{Simons1997,Pike2006} by coordinated manipulation of focal adhesions. The pipette was 
functionalized with fibronectin, gangliosides were fluorescently labeled, the pipette deformed the 
focal adhesion side and the behavior of the fluorescently labeled gangliosides were detected. This 
was seen as a hint, how membrane rafts reacted \cite{Fuentes2012}.

@@

Beside these more or less \emph{direct} combinations and correlations, which are displaying images 
obtained by SICM and fluorescence microscopy of the same cell/same region, also \emph{indirect} 
correlations exist. They are showing images under comparable conditions and extent the 
investigation to aspects, which could not be obtained by using one technique alone. Such 
\emph{indirect} correlations were used for investigating the uptake of nanotubes \cite{Lee2013}, 
nanoparticles \cite{Gesper2017} or for investigating healthy and failing myocytes \cite{Lyon2009}. 
Nevertheless is it important to mention, that they could just giving hints of correlations, it 
is not directly comparable with investigations of both in the same cell.
